On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-05 tt_theorem.tex
12/5 evening...

	Finally, we prove Statement 3.
	In order for $w[i]$ not to bind, $w[i-2]$ must have already used up its hands.
	The bead $w[i-1]$ consumes one hand and provides nothing.
	Thus,  $\#bc(C_{i-3}) - 1 \geq \#bc(C_{i})$.
	The bead $w[i+1]$ consumes one hand and provides nothing.
	Finally, $w[i+2]$ uses one hand of $w[i]$, and hence, does not increase the binding capability.
	Therefore, $\#bc(C_{i-3}) -2 \geq \#bc(C_{i+2})$.
	This argument actually works also for the case when $w[i]$ is stabilized rather by binding. \qed
\end{proof}

@@

\proof{Proof of Tunnel Troll Theorem}

Let us first consider cases of $\delta \geq 3, \alpha = 1$. 
See Fig.~\ref{TTT_tunnel_exit}. Consider the stabilization of $w[i]$. 
This bead $w[i]$, once stabilized, shares two neighbors with its predecessor $w[i-1]$, which are denoted by $n_3, n_4$. 
Both of them have been already occupied because $S[i] = t$.

@@

Assume $w[i]$ forms no bond.
If $S[i] \in \{t_s, t_o\}$, Lemmas~\ref{TTT_exit} and \ref{TTT_tunnelC_lemma} imply $\#bc(C_{i-2}) > \#bc(C_{i+2})$.
Observe that the bead $w[i-1]$ is at the entrance of the previous tunnel or inside.
It is when a bead is stabilized at the entrance of a tunnel that the troll of the tunnel decreases binding capability.
Thus, the inequality does not rely on the troll of previous tunnel.
If $S[i] = t_a$, Lemma~\ref{TTT_tunnelC_lemma} implies $\#bc(C_{i-3}) - 2 \geq \#bc(C_{i+2})$.
%The previous tunnel must be indeed a tunnel section of type A (see Fig.~\ref{TTT_tunnelC_enter_usingBond}).
This inequality involves two tunnels but its difference 2 enables us to consider that binding capability decreases by 1 through this tunnel. \qed

@@

\begin{theorem}[$\delta = 1, \alpha = 4$]
Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 4$. It can yield only finite conformation of length is $3n^2  + 3n + 1$.
\end{theorem}

@@

\begin{theorem}[$\delta = 1, \alpha = 3$]
Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 3$. It can yield only finite conformations of length is $4n + 14$.
\end{theorem}

@@

\begin{theorem}[$\delta= 1, \alpha=2$]
Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 2$. It can yield infinite structures but they are only zig-zag conformation in $w[27n^2 + 9n + 1]$.
\end{theorem}

>>>>

	We finalize this proof by showing Statement 3.
	In order for $w[i]$ not to bind, $w[i-2]$ must have already used up its hands.
	The bead $w[i-1]$ consumes one hand and provides nothing.
	Thus,  $\#bc(C_{i-3}) - 1 \geq \#bc(C_{i})$.
	The bead $w[i+1]$ consumes one hand and provides nothing.
	Finally, $w[i+2]$ uses one hand of $w[i]$, and hence, does not increase the binding capability.
	Therefore, $\#bc(C_{i-3}) -2 \geq \#bc(C_{i+2})$.
	This argument actually works also for the case when $w[i]$ is stabilized rather by binding. \qed
\end{proof}

@@

Now we are ready to prove the Tunnel Troll Theorem.

\begin{proof}%{Proof of Tunnel Troll Theorem}
Let us first consider cases of $\delta \geq 3, \alpha = 1$. 
See Fig.~\ref{TTT_tunnel_exit}. Consider the stabilization of $w[i]$. 
This bead $w[i]$, once stabilized, shares two neighbors with its predecessor $w[i-1]$, which are denoted by $n_3, n_4$. 
Both of them have been already occupied because $S[i] = t$.

@@

Assume $w[i]$ forms no bond.
If $S[i] \in \{t_s, t_o\}$, Lemmas~\ref{TTT_exit} and \ref{TTT_tunnelC_lemma} imply $\#bc(C_{i-2}) > \#bc(C_{i+2})$.
Observe that the bead $w[i-1]$ is at the entrance of the previous tunnel or inside.
It is when a bead is stabilized at the entrance of a tunnel that the troll of the tunnel decreases binding capability.
Thus, the inequality does not rely on the troll of previous tunnel.
If $S[i] = t_a$, Lemma~\ref{TTT_tunnelC_lemma} implies $\#bc(C_{i-3}) - 2 \geq \#bc(C_{i+2})$.
%The previous tunnel must be indeed a tunnel section of type A (see Fig.~\ref{TTT_tunnelC_enter_usingBond}).
This inequality involves two tunnels but its difference 2 enables us to consider that binding capability decreases by 1 through this tunnel. \qed
\end{proof}

@@

\begin{theorem}[$\delta = 1, \alpha = 4$]
Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 4$. It can yield only finite conformation of length $3n^2  + 3n + 1$.
\end{theorem}

@@

\begin{theorem}[$\delta = 1, \alpha = 3$]
Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 3$. It can yield only finite conformations of length $4n + 14$.
\end{theorem}

@@

\begin{theorem}[$\delta= 1, \alpha=2$]
Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 2$.
It can yield an infinite structure, but the transcript folds into the zig-zag conformation after its ($27n^2 + 9n +1$)-th bead.
\end{theorem}
